Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
people need no invitation for criticism
passive

My consideration of transparency centers around the use of induction to test imprecise theories.
A theory is imprecise because it must be refined using data to make testable statements.
I conceptualize induction to derive testable statements as choosing among a set of implications of the theory.
Such a set of possible implications and the process of choosing among them according to a loss function is what I understand as a model.
However, this conceptualization may be criticized.
It is not entirely clear how to chose the process of selecting the best fitting version of the theory.
Should the process of induction depend on the theory?
Is the application of mathematically or computationally convenient methods, as is usual in statistical modeling, sufficient?
Must we account for the arbitrariness of the selection process?

@@

It might happen that in the end, more than one inductive process may be applicable, and no criterium makes one preferable over the other, i.e., from the point of the researcher, the decision is arbitrary.
We have dealt with arbitrary assumptions by choosing an inductive process and forming the expectation over all possible data.
A possible direction for future research is to explore if forming the expectation over inductive processes is similarly fruitful.
One suggestion in such a direction is a method called multiverse analysis [@steegenIncreasingTransparencyMultiverse2016], where many different data analytic decisions are systematically explored.

>>>>

My consideration of transparency centers around the use of induction to test imprecise theories.
A theory is imprecise because it must be refined using data to make testable statements.
I conceptualize induction to derive testable statements as choosing among a set of implications of the theory.
Such a set of possible implications and the process of choosing among them according to a loss function is what I understand as a model.
It is not entirely clear how to chose the process of selecting the best fitting version of the theory.
Should the process of induction depend on the theory?
Is the application of mathematically or computationally convenient methods, as is usual in statistical modeling, sufficient?
Does the arbitrariness of the selection process needs to be accounted for?

@@

It might happen that in the end, more than one inductive process may be applicable, and no criterium makes one preferable over the other, i.e., from the point of the researcher, the decision is arbitrary.
It has been dealt with arbitrary assumptions by choosing an inductive process and forming the expectation over all possible data.
A possible direction for future research is to explore if forming the expectation over inductive processes is similarly fruitful.
One suggestion in such a direction is a method called multiverse analysis [@steegenIncreasingTransparencyMultiverse2016], where many different data analytic decisions are systematically explored.
